Reading main files and preparing data sets

### 2025-04-04 README.Rmd
inclusion of section for python integration and how to use this package

To reduce the barriers to the use of the Public Use Microdata Files, this data product has extracted all walking and cycling episodes and their corresponding episode weights. Origins and destinations are categorized, and it is possible to investigate active travel (number of episodes and their duration) for broad categories of purposes (e.g., travel to work or school, travel to other's home).

The data covers cycles Cycles 2 (1986), 7 (1992), 12 (1998), 19 (2005), 24 (2010), and 29 (2015), spanning a period of almost thirty years.

>>>>

To reduce the barriers to the use of the Public Use Microdata Files, this data product has extracted all walking and cycling episodes and their corresponding episode weights. Origins and destinations are categorized, and it is possible to investigate active travel (number of episodes and their duration) for broad categories of purposes (e.g., travel to work or school, travel to other's home). {ActiveCA} also include some socioeconomic variables from the GSS Main Files to facilitate profiling the survey's respondents.

The data covers cycles Cycles 2 (1986), 7 (1992), 12 (1998), 19 (2005), 24 (2010), 29 (2015), and 2022, spanning a period of more than thirty five years.

### 2025-04-04 data-raw/01-preprocessing-episode-files.Rmd

walking_2022 <- walking_2022 |> 
  left_join(gss_m_2022, by = 'PUMFID') |>  # Merging the two tables
  dplyr::select(names(walking_2015))

@@

Now, let's select only the cases of respondents who live in a CMA or CA:
```{r}
cycling_2022 <- cycling_2022 |> 
  left_join(gss_m_2022, by = 'PUMFID') |>  # Merging the two tables
  dplyr::select(names(walking_2015))

>>>>

walking_2022 <- walking_2022 |> 
  left_join(gss_m_2022, by = 'PUMFID') |>  # Merging the two tables
  dplyr::select(names(walking_2015)) %>% 
  mutate(PUMFID = as.numeric(as.character(PUMFID)),
         WGHT_EPI = as.numeric(as.character(WGHT_EPI)))

@@

Now, let's select only the cases of respondents who live in a CMA or CA:
```{r}
cycling_2022 <- cycling_2022 |> 
  left_join(gss_m_2022, by = 'PUMFID') |>  # Merging the two tables
  dplyr::select(names(walking_2015)) %>% 
  mutate(PUMFID = as.numeric(as.character(PUMFID)),
         WGHT_EPI = as.numeric(as.character(WGHT_EPI)))

### 2025-04-04 data-raw/02-calculating-impedances.Rmd

This Rmarkdown file is part of the
[**ActiveCA**](https://github.com/dias-bruno/ActiveCA) package.The main objective of the *ActiveCA* package is to identify the most
appropriate impedance functions for active transportation modes for
various destinations and time periods in Canada. To do achieve our
objective, we analyzed historical data from the [General Social Survey
(GSS)](https://www23.statcan.gc.ca/imdb/p2SV.pl?Function=getSurvey&SDDS=5221)
from 1986 to 2015 in Canada to calculate the impedance function for
cycling and walking trips.

>>>>

This Rmarkdown file is part of the
[**ActiveCA**](https://github.com/dias-bruno/ActiveCA) package.The main objective of the *ActiveCA* package is to identify the most
appropriate impedance functions for active transportation modes for
various destinations and time periods in Canada. To do achieve our
objective, we analyzed historical data from the [General Social Survey
(GSS)](https://www23.statcan.gc.ca/imdb/p2SV.pl?Function=getSurvey&SDDS=5221)
from 1986 to 2022 in Canada to calculate the impedance function for
cycling and walking trips.

### 2025-04-04 data-raw/03-preprocessing-main-files.Rmd

```{r filtering-variables-2022}
gss_main_2022 <- gss_m_2022 %>%
  dplyr::select("PUMFID", "WGHT_PER","SURVMNTH", "PRV", "LUC_RST", "REGION",  "HSDSIZEC","AGEGR10", "GENDER2",
"MARSTAT", "PHSDFLG", "AGEPRC",  "GENPR2",  "COUPGEN2","CHH0017C","CHH0004C","CHH0514C","CHH1517C","CXRFLAG",
"PARNUM",  "SENFLAG", "MULTIGEN","DDEV_FL", "DDEX_FL", "DFLEX_FL","DHEAR_FL","DLRN_FL", "DMEM_FL", "DMENT_FL",
 "DMOB_FL", "DPAIN_FL","DUNK_FL", "DVIS_FL", "DDIS_FL", "DTYPER",  "DCLASS",  "TCS_110", "TCS_120", "TCS_130",
 "TCS_140", "TCS_150", "TCS_160", "TCS_170", "TCS_180", "TCS_190", "TCS_200",  "GEN_01",  "GEN_02",  "SRS_10",  "MSS_130", "ACT7DAYC","MRW_05C", "MRW_D40A",
"MRW_D40B","WET_120",  "WHW_230", "WHWD140G","TLWK_01A","TLWK_06","WLYD170G",
"ATT_120", "ATT_130", "ATT_131",
"ATT_150C","ATT_160", "ATT_170",
"CTW_140A","CTW_140B","CTW_140C","CTW_140D",
"CTW_140E","CTW140GR","CTW_140I","CTW_150G","CTW_160", "CTW_170", "CTW_180", "CTW_190", "CTW_210", "CTW_215",
"ED_05",  "MAP_110C","MAP_D40A","DOR_110C","IM_01A",  "YRARRI_C","BPP_01A", "BPR_20", "ABM_01A",
"AIP_01A", "VISMINFL","VISPRFL", "REL_02",  "RELIGFLG","INC_C",  
"FAMINC_C","GTU_110", "GTU_130",  "DDAY",  "DVTDAY")
```

>>>>

```{r filtering-variables-2022}
gss_main_2022 <- gss_m_2022 %>%
  dplyr::select("PUMFID", "WGHT_PER","SURVMNTH", "PRV", "LUC_RST", "REGION",  "HSDSIZEC","AGEGR10", "GENDER2",
"MARSTAT", "PHSDFLG", "AGEPRC",  "GENPR2",  "COUPGEN2","CHH0017C","CHH0004C","CHH0514C","CHH1517C","CXRFLAG",
"PARNUM",  "SENFLAG", "MULTIGEN","DDEV_FL", "DDEX_FL", "DFLEX_FL","DHEAR_FL","DLRN_FL", "DMEM_FL", "DMENT_FL",
 "DMOB_FL", "DPAIN_FL","DUNK_FL", "DVIS_FL", "DDIS_FL", "DTYPER",  "DCLASS",  "TCS_110", "TCS_120", "TCS_130",
 "TCS_140", "TCS_150", "TCS_160", "TCS_170", "TCS_180", "TCS_190", "TCS_200",  "GEN_01",  "GEN_02",  "SRS_10",  "MSS_130", "ACT7DAYC","MRW_05C", "MRW_D40A",
"MRW_D40B","WET_120",  "WHW_230", "WHWD140G","TLWK_01A","TLWK_06","WLYD170G",
"ATT_120", "ATT_130", "ATT_131",
"ATT_150C","ATT_160", "ATT_170",
"CTW_140A","CTW_140B","CTW_140C","CTW_140D",
"CTW_140E","CTW140GR","CTW_140I","CTW_150G","CTW_160", "CTW_170", "CTW_180", "CTW_190", "CTW_210", "CTW_215",
"ED_05",  "MAP_110C","MAP_D40A","DOR_110C","IM_01A",  "YRARRI_C","BPP_01A", "BPR_20", "ABM_01A",
"AIP_01A", "VISMINFL","VISPRFL", "REL_02",  "RELIGFLG","INC_C",  
"FAMINC_C","GTU_110", "GTU_130",  "DDAY",  "DVTDAY") %>% 
  mutate(PUMFID = as.numeric(as.character(PUMFID)),
         WGHT_PER = as.numeric(as.character(WGHT_PER)))
```
